Improving credibility and efficiency of decision-making \\ within democratic communities via statistical quorum

### 2018-04-19 statistical-quorum.tex
Fixing.
Updated authors.
Addresses.
Enable review mode.
Set language.
Added CSS concepts.

\documentclass[format=acmsmall, review=false, screen=true, anonymous=false]{acmart}

@@

\author{Gang Zhou}
\orcid{1234-5678-9012-3456}
\affiliation{%
  \institution{College of William and Mary}
  \streetaddress{104 Jamestown Rd}
  \city{Williamsburg}
  \state{VA}
  \postcode{23185}
  \country{USA}}
\email{gang_zhou@wm.edu}
\author{Valerie B\'eranger}
\affiliation{%
  \institution{Inria Paris-Rocquencourt}
  \city{Rocquencourt}
  \country{France}
}
\email{beranger@inria.fr}
\author{Aparna Patel}
\affiliation{%
 \institution{Rajiv Gandhi University}
 \streetaddress{Rono-Hills}
 \city{Doimukh}
 \state{Arunachal Pradesh}
 \country{India}}
\email{aprna_patel@rguhs.ac.in}
\author{Huifen Chan}
\affiliation{%
  \institution{Tsinghua University}
  \streetaddress{30 Shuangqing Rd}
  \city{Haidian Qu}
  \state{Beijing Shi}
  \country{China}
}
\email{chan0345@tsinghua.edu.cn}
\author{Ting Yan}
\affiliation{%
  \institution{Eaton Innovation Center}
  \city{Prague}
  \country{Czech Republic}}
\email{yanting02@gmail.com}
\author{Tian He}
\affiliation{%
  \institution{University of Virginia}
  \department{School of Engineering}
  \city{Charlottesville}
  \state{VA}
  \postcode{22903}
  \country{USA}
}
\affiliation{%
  \institution{University of Minnesota}
  \country{USA}}
\email{tinghe@uva.edu}
\author{Chengdu Huang}
\author{John A. Stankovic}
\author{Tarek F. Abdelzaher}
\affiliation{%
  \institution{University of Virginia}
  \department{School of Engineering}
  \city{Charlottesville}
  \state{VA}
  \postcode{22903}
  \country{USA}
}

@@

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

@@

Let
\begin{description}
\begin{itemize}
\item[$C = $] $\{X_1,\ldots, X_n\}$, the set of competing proposals,
\item[$N = $] population size,
\item[$X_i = $] $\{v_1, \ldots, v_{m_i}\}$, the $m_i$ raw votes for proposal $i$, after excluding abstentions,
\item[$N_i = $] $(N - \textrm{number of abstentions on } X_i)$, the effective population voting on proposal $X_i$,
\item[$\alpha_i = $] $\sum\limits_{v \in X_i}\left(\frac{v+1}{2}\right)$, the effective number of ``yes'' votes on motion $X_i$,
\item[$\beta_i = $] $m_i - \alpha_i$, the effective number of ``no'' votes on motion $X_i$,
\item[$K_i = $] $N_i - m_i$, the number of remaining votes yet to be cast on $X_i$,
\item[$p_i = $] true latent community bias towards voting ``yes'' on $X_i$.
\end{itemize}
\end{description}

@@

When considering a single proposal $X_i$ in isolation, we wish to compute:
\begin{align}\label{eq1}
\Pr(\alpha^*_i > T_i \mid X_i),
\end{align}
where
\begin{description}
\begin{itemize}
\item[$\alpha^*_i = $] the total number of ``yes'' votes for $X_i$ if we were to sample the entire population,
\item[$T_i = $] $f \cdot N_i$, for some fraction $f$ corresponding to the type of majority needed for the vote
(e.g., $f=\frac{1}{2}$ for a simple majority).
\end{itemize}
\end{description}
Using a desirable prior
\begin{align}\label{eq2}
p_i \mid X_i \sim \operatorname{Beta}(1+\frac{\alpha_i}{K_i},1+\frac{\beta_i}{K_i}),
\end{align}
corresponding to a uniform prior when no votes have been cast ($\alpha_i = \beta_i = 0$), we can express \eqref{eq1} as:
\begin{align}\label{eq3}
\Pr(\alpha^*_i > T_i \mid X_i) &= 1 - {CDF}_{\nu_i}(V_i)
\end{align}
for
\begin{align*}
&\nu_i \sim \operatorname{Beta-Binomial}(1 + \frac{\alpha_i}{K_i}c, 1 + \frac{\beta_i}{K_i}c, K_i),\\
&{CDF}_{\nu_i}(V_i)  = \Pr(\nu_i \leq V_i),
\end{align*}
\todo[inline]{Note that we choose $c=10$ because it leads to intuitive results.}
where
\begin{description}
\begin{itemize}
\item[$V_i = $] $\lfloor{T_i - \alpha_i}\rfloor$, the maximum number of additional ``yes'' votes $X_i$ could receive such that it would remain below threshold.
\end{itemize}
\end{description}

@@

Under the assumption that the community's votes on motions are independent across motions (which, in many instances, will actually give a lower bound on \eqref{eq3} when a community's support of one proposal is negatively correlated with its support on a competing proposal), we can decompose \eqref{eq3} as follows:
\begin{align}\label{eq5}
& \Pr\left(\bigwedge_{j \neq i} (\alpha^*_i > \alpha^*_j) \mid C\right) \nonumber \\
= & \prod_{j \neq i}\left(1 - \sum_{k=\lceil\delta_{ij}\rceil}^{K_j} \Pr(\nu_j = k) \cdot {CDF}_{\nu_i}(\alpha_j + k) \right)
\end{align}
where
\begin{description}
\begin{itemize}
\item[$\delta_{ij} = $] $\alpha_i - \alpha_j$, the number of effective ``yes'' votes $X_i$ leads $X_j$ by.
\end{itemize}
\end{description}

@@

For our purposes, we make a natural choice,
\begin{align}\label{eq6}
\lambda (t) = \lambda_0 {(\gamma)}^{\frac{t}{K_i/N_i}},
\end{align}
where
\begin{description}
\begin{itemize}
\item[$\lambda_0 =$] a time-averaged rate of vote arrivals (preferably over a unit of time that sufficiently smooths the historical rate),
\item[$\gamma =$] a decay factor ($0 < \gamma < 1$) ideally tuned to fit real historical data for the community via a regression analysis.
\end{itemize}
\end{description}
Now, for example, to upper bound with $95\%$ probability the remaining number of votes still pending, we wish to solve for $\hat{K_i}$ such that the following inequality is satisfied:
\begin{align}\label{eq7}
\lim_{t\rightarrow \infty}\Pr\left(N(t)\leq \hat{K_i}\right) & = \sum_{n=0}^{\hat{K_i}} \frac{\Lambda^n}{n!}e^{-\Lambda} \geq 95\%,
\end{align}
where $\Lambda = \frac{\lambda_0 \cdot K_i/N_i)}{\ln{1/\gamma}}$.
Upon solving for $\hat{K_i}$, we update $N_i \leftarrow \min\{N_i,\alpha_i + \beta_i + \hat{K_i}\}$, and can proceed to check for a statistical quorum using Eq. \ref{eq5}.

@@

\section{Derivation of Eq. \eqref{eq2}}
In choosing a Beta prior, we start with $\operatorname{Beta}(1,1)$, as it represents the uniform distribution over all potential values of the community's bias.  To update the prior based on collected votes, standard theory suggests updating to $\operatorname{Beta}(1+\alpha_i,1+\beta_i)$; however, there are a few consistency issues with this update that we seek to fix:
\begin{description}
\begin{itemize}
\item[$(1)$] The updated prior should not depend on the absolute number of votes $\alpha_i$, $\beta_i$, as this is not scale-invariant; rather, it should depend on the relative proportions (which are unitless instead of a number of votes),
\item[$(2)$] as $\alpha_i + \beta_i \rightarrow N_i$, $\mathbb{E}[p_i] \rightarrow \frac{\alpha_i}{\alpha_i+\beta_i}$ (at a rate independent of $N_i$),
\item[$(3)$] as $\alpha_i + \beta_i \rightarrow N_i$, $\operatorname{Var}[p_i] \rightarrow 0$ (at a rate independent of $N_i$).
\end{itemize}
\end{description}
To satisfy these consistency properties, we seek to linearly update the prior's scale parameters in a more natural way: $\operatorname{Beta}(1+\eta\alpha_i,1+\eta\beta_i)$ for some renormalizing factor $\eta$.

@@

\section{Derivation of Eq. \eqref{eq6}}
The properties we desire for $\lambda(t)$ are:
\begin{description}
\begin{itemize}
\item[$(1)$] as $K_i \rightarrow 0$, the rate of incoming votes should drop exponentially and should be independent of $N_i$,
\item[$(2)$] as $t \rightarrow \infty$, the rate of incoming votes should drop exponentially.
\end{itemize}
\end{description}
Setting $\lambda (t) = \lambda_0 {(\gamma)}^{\frac{t}{K_i/N_i}}$ for $0 < \gamma < 1$ satisfies these constraints while still allowing for the exact rate to be tunable.

\section{Derivation of Eq. \eqref{eq7}}
Using $\lambda (t) = \lambda_0 {(\gamma)}^{\frac{t}{K_i/N_i}}$, we have
\begin{align*}
\lim_{t \rightarrow \infty} \Lambda (t) &=\int _{0}^{\infty}\lambda (t)\mathrm{d}t\\
&= \int _{0}^{\infty} \lambda_0 {(\gamma)}^{\frac{t}{K_i/N_i}} \mathrm{d}t\\
&= \lambda_0 \frac{K_i/N_i}{\ln{1/\gamma}}.
\end{align*}
Thus,
\begin{align*}
\lim_{t\rightarrow \infty}\Pr\left(N(t) = n\right) = \frac{(\lambda_0 \cdot K_i/N_i)^n}{n!(\ln{1/\gamma})^n}e^{-\lambda_0 \frac{K_i/N_i}{\ln{1/\gamma}}},
\end{align*}
and
\begin{align*}
\lim_{t\rightarrow \infty}\Pr\left(N(t)\leq \hat{K_i}\right) & = \sum_{n=0}^{\hat{K_i}} \frac{(\lambda_0 \cdot K_i/N_i)^n}{n!(\ln{1/\gamma})^n}e^{-\lambda_0 \frac{K_i/N_i}{\ln{1/\gamma}}}.
\end{align*}
\end{document}

@@

>>>>

\documentclass[format=acmsmall, review=true, screen=true, anonymous=true]{acmart}

\usepackage[english]{babel}

@@

\author{Mitar Milutinovic}
\affiliation{%
  \institution{UC Berkeley}}
\email{mitar@cs.berkeley.edu}
\author{Maxinder S. Kanwal}
\affiliation{%
  \institution{UC Berkeley}}
\email{maxowaxo2013@gmail.com}
\author{David Marn}
\affiliation{%
  \institution{UC Berkeley}}
\email{david.marn@gmail.com}

@@

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below.
%
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10003120.10003130.10003131.10003570</concept_id>
<concept_desc>Human-centered computing~Computer supported cooperative work</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10003120.10003130.10011764</concept_id>
<concept_desc>Human-centered computing~Collaborative and social computing devices</concept_desc>
<concept_significance>500</concept_significance>
</concept>
<concept>
<concept_id>10010405.10010476.10010936.10003590</concept_id>
<concept_desc>Applied computing~Voting / election technologies</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Human-centered computing~Computer supported cooperative work}
\ccsdesc[500]{Human-centered computing~Collaborative and social computing devices}
\ccsdesc[500]{Applied computing~Voting / election technologies}

@@

Let
\begin{description}
\item[$C = $] $\{X_1,\ldots, X_n\}$, the set of competing proposals,
\item[$N = $] population size,
\item[$X_i = $] $\{v_1, \ldots, v_{m_i}\}$, the $m_i$ raw votes for proposal $i$, after excluding abstentions,
\item[$N_i = $] $(N - \textrm{number of abstentions on } X_i)$, the effective population voting on proposal $X_i$,
\item[$\alpha_i = $] $\sum\limits_{v \in X_i}\left(\frac{v+1}{2}\right)$, the effective number of ``yes'' votes on motion $X_i$,
\item[$\beta_i = $] $m_i - \alpha_i$, the effective number of ``no'' votes on motion $X_i$,
\item[$K_i = $] $N_i - m_i$, the number of remaining votes yet to be cast on $X_i$,
\item[$p_i = $] true latent community bias towards voting ``yes'' on $X_i$.
\end{description}

@@

When considering a single proposal $X_i$ in isolation, we wish to compute:
\begin{align}\label{eq1}
\Pr(\alpha^*_i > T_i \mid X_i),
\end{align}
where
\begin{description}
\item[$\alpha^*_i = $] the total number of ``yes'' votes for $X_i$ if we were to sample the entire population,
\item[$T_i = $] $f \cdot N_i$, for some fraction $f$ corresponding to the type of majority needed for the vote
(e.g., $f=\frac{1}{2}$ for a simple majority).
\end{description}
Using a desirable prior
\begin{align}\label{eq2}
p_i \mid X_i \sim \operatorname{Beta}(1+\frac{\alpha_i}{K_i},1+\frac{\beta_i}{K_i}),
\end{align}
corresponding to a uniform prior when no votes have been cast ($\alpha_i = \beta_i = 0$), we can express \eqref{eq1} as:
\begin{align}\label{eq3}
\Pr(\alpha^*_i > T_i \mid X_i) &= 1 - {CDF}_{\nu_i}(V_i)
\end{align}
for
\begin{align*}
&\nu_i \sim \operatorname{Beta-Binomial}(1 + \frac{\alpha_i}{K_i}c, 1 + \frac{\beta_i}{K_i}c, K_i),\\
&{CDF}_{\nu_i}(V_i)  = \Pr(\nu_i \leq V_i),
\end{align*}
\todo[inline]{Note that we choose $c=10$ because it leads to intuitive results.}
where
\begin{description}
\item[$V_i = $] $\lfloor{T_i - \alpha_i}\rfloor$, the maximum number of additional ``yes'' votes $X_i$ could receive such that it would remain below threshold.
\end{description}

@@

Under the assumption that the community's votes on motions are independent across motions (which, in many instances, will actually give a lower bound on \eqref{eq3} when a community's support of one proposal is negatively correlated with its support on a competing proposal), we can decompose \eqref{eq3} as follows:
\begin{align}\label{eq5}
& \Pr\left(\bigwedge_{j \neq i} (\alpha^*_i > \alpha^*_j) \mid C\right) \nonumber \\
= & \prod_{j \neq i}\left(1 - \sum_{k=\lceil\delta_{ij}\rceil}^{K_j} \Pr(\nu_j = k) \cdot {CDF}_{\nu_i}(\alpha_j + k) \right)
\end{align}
where
\begin{description}
\item[$\delta_{ij} = $] $\alpha_i - \alpha_j$, the number of effective ``yes'' votes $X_i$ leads $X_j$ by.
\end{description}

@@

For our purposes, we make a natural choice,
\begin{align}\label{eq6}
\lambda (t) = \lambda_0 {(\gamma)}^{\frac{t}{K_i/N_i}},
\end{align}
where
\begin{description}
\item[$\lambda_0 =$] a time-averaged rate of vote arrivals (preferably over a unit of time that sufficiently smooths the historical rate),
\item[$\gamma =$] a decay factor ($0 < \gamma < 1$) ideally tuned to fit real historical data for the community via a regression analysis.
\end{description}
Now, for example, to upper bound with $95\%$ probability the remaining number of votes still pending, we wish to solve for $\hat{K_i}$ such that the following inequality is satisfied:
\begin{align}\label{eq7}
\lim_{t\rightarrow \infty}\Pr\left(N(t)\leq \hat{K_i}\right) & = \sum_{n=0}^{\hat{K_i}} \frac{\Lambda^n}{n!}e^{-\Lambda} \geq 95\%,
\end{align}
where $\Lambda = \frac{\lambda_0 \cdot K_i/N_i)}{\ln{1/\gamma}}$.
Upon solving for $\hat{K_i}$, we update $N_i \leftarrow \min\{N_i,\alpha_i + \beta_i + \hat{K_i}\}$, and can proceed to check for a statistical quorum using Eq. \ref{eq5}.

@@

\section{Derivation of Eq. \eqref{eq2}}
In choosing a Beta prior, we start with $\operatorname{Beta}(1,1)$, as it represents the uniform distribution over all potential values of the community's bias.  To update the prior based on collected votes, standard theory suggests updating to $\operatorname{Beta}(1+\alpha_i,1+\beta_i)$; however, there are a few consistency issues with this update that we seek to fix:
\begin{description}
\item[$(1)$] The updated prior should not depend on the absolute number of votes $\alpha_i$, $\beta_i$, as this is not scale-invariant; rather, it should depend on the relative proportions (which are unitless instead of a number of votes),
\item[$(2)$] as $\alpha_i + \beta_i \rightarrow N_i$, $\mathbb{E}[p_i] \rightarrow \frac{\alpha_i}{\alpha_i+\beta_i}$ (at a rate independent of $N_i$),
\item[$(3)$] as $\alpha_i + \beta_i \rightarrow N_i$, $\operatorname{Var}[p_i] \rightarrow 0$ (at a rate independent of $N_i$).
\end{description}
To satisfy these consistency properties, we seek to linearly update the prior's scale parameters in a more natural way: $\operatorname{Beta}(1+\eta\alpha_i,1+\eta\beta_i)$ for some renormalizing factor $\eta$.

@@

\section{Derivation of Eq. \eqref{eq6}}
The properties we desire for $\lambda(t)$ are:
\begin{description}
\item[$(1)$] as $K_i \rightarrow 0$, the rate of incoming votes should drop exponentially and should be independent of $N_i$,
\item[$(2)$] as $t \rightarrow \infty$, the rate of incoming votes should drop exponentially.
\end{description}
Setting $\lambda (t) = \lambda_0 {(\gamma)}^{\frac{t}{K_i/N_i}}$ for $0 < \gamma < 1$ satisfies these constraints while still allowing for the exact rate to be tunable.

\section{Derivation of Eq. \eqref{eq7}}
Using $\lambda (t) = \lambda_0 {(\gamma)}^{\frac{t}{K_i/N_i}}$, we have
\begin{align*}
\lim_{t \rightarrow \infty} \Lambda (t) &=\int _{0}^{\infty}\lambda (t)\mathrm{d}t\\
&= \int _{0}^{\infty} \lambda_0 {(\gamma)}^{\frac{t}{K_i/N_i}} \mathrm{d}t\\
&= \lambda_0 \frac{K_i/N_i}{\ln{1/\gamma}}.
\end{align*}
Thus,
\begin{align*}
\lim_{t\rightarrow \infty}\Pr\left(N(t) = n\right) = \frac{(\lambda_0 \cdot K_i/N_i)^n}{n!(\ln{1/\gamma})^n}e^{-\lambda_0 \frac{K_i/N_i}{\ln{1/\gamma}}},
\end{align*}
and
\begin{align*}
\lim_{t\rightarrow \infty}\Pr\left(N(t)\leq \hat{K_i}\right) & = \sum_{n=0}^{\hat{K_i}} \frac{(\lambda_0 \cdot K_i/N_i)^n}{n!(\ln{1/\gamma})^n}e^{-\lambda_0 \frac{K_i/N_i}{\ln{1/\gamma}}}.
\end{align*}

@@

\end{document}
